Illusion Game Validation (Study 2)

### 2022-09-01 study2/study2.Rmd
edit
update

cache <- TRUE
runModels <- FALSE
bestModels <- TRUE
fig.width <- see::golden_ratio(7)
fig.height <- 7

@@

```{r outliers_RT, message=FALSE, warning=FALSE, fig.width=20, fig.height=20, cache=cache}
# RT distribution
p <- df |> 
  filter(RT < 10000) |> 
  estimate_density(select = "RT", at = c("Participant", "Block")) |>
  group_by(Participant) |>
  normalize(select = "y") |>
  ungroup() |>
  mutate(Participant = fct_relevel(Participant, as.character(dfsub$Participant))) |> 
  mutate(color = ifelse(Participant %in% outliers, "red", ifelse(Participant %in% partial_outliers, "orange", "blue"))) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(data = normalize(estimate_density(filter(df, RT < 10000), select = "RT"), select = "y"), alpha = 0.2) +
  geom_line(aes(color = color, group = interaction(Participant, Block), linetype = Block)) +
  geom_vline(xintercept = 125, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("red" = "#F44336", "orange" = "#FF9800", "blue" = "blue"), guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  coord_cartesian(xlim = c(0, 3000)) +
  theme_modern() +
  theme(axis.text.y = element_blank()) +
  facet_wrap(~Participant) +
  labs(y = "", x = "Reaction Time (ms)")
p
# ggsave("figures/outliers.png", p, width=25, height=25)

@@

save(model_delboeuf_err, file="models/model_delboeuf_err.Rdata")
```
```{r message=FALSE, warning=FALSE, eval=TRUE}
load("models/model_delboeuf_err.RData")
load("models/gam_delboeuf_err.RData")

@@

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
p_delboeuf_err <- plot_model_err(data, model_delboeuf_err, gam_delboeuf_err)
p_delboeuf_err
```

@@

save(model_delboeuf_rt, file="models/model_delboeuf_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
load("models/model_delboeuf_rt.RData")
load("models/gam_delboeuf_rt.RData")

@@

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
plot_ppcheck(model_delboeuf_rt, gam_delboeuf_rt)

@@

```{r message=FALSE, warning=FALSE, cache=cache, fig.height=fig.height*2, eval=FALSE}
p_delboeuf <- plot_all(data, p_delboeuf_err, p_delboeuf_rt)
p_delboeuf
```

@@

save(model_ebbinghaus_err, file="models/model_ebbinghaus_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_ebbinghaus_err.RData")
load("models/gam_ebbinghaus_err.RData")

@@

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
p_ebbinghaus_err <- plot_model_err(data, model_ebbinghaus_err, gam_ebbinghaus_err)
p_ebbinghaus_err
```

@@

```{r m_rt_ebbinghaus, message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
formula <- brms::bf(
  RT ~ Illusion_Effect / (sqrt(Illusion_Difference) * abs(Illusion_Strength)) +
    poly(ISI, 2) + 
    (1 + Illusion_Effect / (sqrt(Illusion_Difference) * abs(Illusion_Strength)) | Participant),
  sigma ~ Illusion_Effect / (sqrt(Illusion_Difference) * abs(Illusion_Strength)) + 
    poly(ISI, 2) + (1 | Participant),
  beta ~ Illusion_Effect / (sqrt(Illusion_Difference) * abs(Illusion_Strength)) + 
    poly(ISI, 2) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_ebbinghaus_rt, file="models/model_ebbinghaus_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
load("models/model_ebbinghaus_rt.RData")
load("models/gam_ebbinghaus_rt.RData")

@@

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
plot_ppcheck(model_ebbinghaus_rt, gam_ebbinghaus_rt)

p_ebbinghaus_rt <- plot_model_rt(data, model_ebbinghaus_rt, gam_ebbinghaus_rt)
p_ebbinghaus_rt
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, fig.height=fig.height*2, eval=FALSE}
p_ebbinghaus <- plot_all(data, p_ebbinghaus_err, p_ebbinghaus_rt)
p_ebbinghaus
```

@@

save(model_rodframe_err, file="models/model_rodframe_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_rodframe_err.RData")
load("models/gam_rodframe_err.RData")
```

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
p_rodframe_err <- plot_model_err(data, model_rodframe_err, gam_rodframe_err)
p_rodframe_err
```

@@

```{r m_rt_rodframe, message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
formula <- brms::bf(
  RT ~ Illusion_Effect / (logmod(Illusion_Difference) * logmod(abs(Illusion_Strength))) +
    poly(ISI, 2) + 
    (1 + Illusion_Effect / (logmod(Illusion_Difference) * logmod(abs(Illusion_Strength))) | Participant),
  sigma ~ Illusion_Effect / (logmod(Illusion_Difference) * logmod(abs(Illusion_Strength))) + 
    poly(ISI, 2) + (1 | Participant),
  beta ~ Illusion_Effect / (logmod(Illusion_Difference) * logmod(abs(Illusion_Strength))) + 
    poly(ISI, 2) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_rodframe_rt, file="models/model_rodframe_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
load("models/model_rodframe_rt.RData")
load("models/gam_rodframe_rt.RData")

@@

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
plot_ppcheck(model_rodframe_rt, gam_rodframe_rt)

p_rodframe_rt <- plot_model_rt(data, model_rodframe_rt, gam_rodframe_rt)
p_rodframe_rt
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, fig.height=fig.height*2, eval=FALSE}
p_rodframe <- plot_all(data, p_rodframe_err, p_rodframe_rt)
p_rodframe
```

@@

save(model_verticalhorizontal_err, file="models/model_verticalhorizontal_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_verticalhorizontal_err.RData")
load("models/gam_verticalhorizontal_err.RData")

# parameters::parameters(model_verticalhorizontal_err)

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
p_verticalhorizontal_err <- plot_model_err(data, model_verticalhorizontal_err, gam_verticalhorizontal_err)
p_verticalhorizontal_err
```

@@

```{r m_rt_verticalhorizontal, message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
formula <- brms::bf(
  RT ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) +
    poly(ISI, 2) + 
    (1 + Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) | Participant),
  sigma ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) + 
    poly(ISI, 2) + (1 | Participant),
  beta ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) + 
    poly(ISI, 2) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_verticalhorizontal_rt, file="models/model_verticalhorizontal_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
load("models/model_verticalhorizontal_rt.RData")
load("models/gam_verticalhorizontal_rt.RData")

@@

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
p_verticalhorizontal_rt <- plot_model_rt(data, model_verticalhorizontal_rt, gam_verticalhorizontal_rt)
p_verticalhorizontal_rt
```

@@

model_zollner_err <- brms::brm(formula,
  data = data,
  refresh = 0
)

# parameters::parameters(model_zollner_err)

save(model_zollner_err, file="models/model_zollner_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_zollner_err.RData")
load("models/gam_zollner_err.RData")
```

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
p_zollner_err <- plot_model_err(data, model_zollner_err, gam_zollner_err)
p_zollner_err
```

@@

```{r m_rt_zollner, message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
formula <- brms::bf(
  RT ~  Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) +
    poly(ISI, 2) + 
    (1 + Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) | Participant),
  sigma ~  Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) +
    poly(ISI, 2) + (1 | Participant),
  beta ~ Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) +
    poly(ISI, 2) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_zollner_rt, file="models/model_zollner_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
load("models/model_zollner_rt.RData")
load("models/gam_zollner_rt.RData")

@@

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
p_zollner_rt <- plot_model_rt(data, model_zollner_rt, gam_zollner_rt)
p_zollner_rt
```

@@

save(model_white_err, file="models/model_white_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_white_err.RData")
load("models/gam_white_err.RData")
```

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
p_white_err <- plot_model_err(data, model_white_err, gam_white_err)
p_white_err
```

@@

```{r m_rt_white, message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
formula <- brms::bf(
  RT ~ Illusion_Effect / (Illusion_Difference * sqrt(abs(Illusion_Strength))) +
    poly(ISI, 2) + 
    (1 + Illusion_Effect / (Illusion_Difference * sqrt(abs(Illusion_Strength))) | Participant),
  sigma ~ Illusion_Effect / (Illusion_Difference * sqrt(abs(Illusion_Strength))) +
    poly(ISI, 2) + (1 | Participant),
  beta ~ Illusion_Effect / (Illusion_Difference * sqrt(abs(Illusion_Strength))) +
    poly(ISI, 2) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_white_rt, file="models/model_white_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
load("models/model_white_rt.RData")
load("models/gam_white_rt.RData")

@@

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
p_white_rt <- plot_model_rt(data, model_white_rt, gam_white_rt)
p_white_rt
```

@@

save(model_mullerlyer_err, file="models/model_mullerlyer_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_mullerlyer_err.RData")
load("models/gam_mullerlyer_err.RData")
```

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
p_mullerlyer_err <- plot_model_err(data, model_mullerlyer_err, gam_mullerlyer_err)
p_mullerlyer_err
```

@@

```{r m_rt_mullerlyer, message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
formula <- brms::bf(
  RT ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) +
    poly(ISI, 2) + 
    (1 + Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) | Participant),
  sigma ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) +
    poly(ISI, 2) + (1 | Participant),
  beta ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) + 
    poly(ISI, 2) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_mullerlyer_rt, file="models/model_mullerlyer_rt.Rdata")
# parameters::parameters(model_white_err)
```
```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
load("models/model_mullerlyer_rt.RData")
load("models/gam_mullerlyer_rt.RData")

@@

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
p_mullerlyer_rt <- plot_model_rt(data, model_mullerlyer_rt, gam_mullerlyer_rt)
p_mullerlyer_rt
```

@@

save(model_ponzo_err, file="models/model_ponzo_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_ponzo_err.RData")
load("models/gam_ponzo_err.RData")
```

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
p_ponzo_err <- plot_model_err(data, model_ponzo_err, gam_ponzo_err)
p_ponzo_err
```

@@

save(model_ponzo_rt, file="models/model_ponzo_rt.Rdata")
# parameters::parameters(model_white_err)
```
```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
load("models/model_ponzo_rt.RData")
load("models/gam_ponzo_rt.RData")

@@

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
p_ponzo_rt <- plot_model_rt(data, model_ponzo_rt, gam_ponzo_rt)
p_ponzo_rt
```

@@

save(model_poggendorff_err, file="models/model_poggendorff_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_poggendorff_err.RData")
load("models/gam_poggendorff_err.RData")
```

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
p_poggendorff_err <- plot_model_err(data, model_poggendorff_err, gam_poggendorff_err)
p_poggendorff_err
```

@@

```{r m_rt_poggendorff, message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
formula <- brms::bf(
  RT ~ Illusion_Effect / (cbrtmod(Illusion_Difference) * sqrt(abs(Illusion_Strength))) +
    poly(ISI, 2) + 
    (1 + Illusion_Effect / (cbrtmod(Illusion_Difference) * sqrt(abs(Illusion_Strength))) | Participant),
  sigma ~ Illusion_Effect / (cbrtmod(Illusion_Difference) * sqrt(abs(Illusion_Strength))) + 
    poly(ISI, 2) + (1 | Participant),
  beta ~ Illusion_Effect / (cbrtmod(Illusion_Difference) * sqrt(abs(Illusion_Strength))) + 
    poly(ISI, 2) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_ponzo_rt, file="models/model_poggendorff_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
load("models/model_poggendorff_rt.RData")
load("models/gam_poggendorff_rt.RData")

@@

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
p_poggendorff_rt <- plot_model_rt(data, model_poggendorff_rt, gam_poggendorff_rt)
p_poggendorff_rt
```

@@

model_contrast_err <- brms::brm(formula,
  data = data,
  refresh = 50
)

@@

save(model_contrast_err, file="models/model_contrast_err.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_contrast_err.RData")
load("models/gam_contrast_err.RData")
```

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache}
p_contrast_err <- plot_model_err(data, model_contrast_err, gam_contrast_err)
p_contrast_err
```

@@

save(model_contrast_rt, file="models/model_contrast_rt.Rdata")
```
```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
load("models/model_contrast_rt.RData")
load("models/gam_contrast_rt.RData")

@@

##### Model Visualization

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
p_contrast_rt <- plot_model_rt(data, model_contrast_rt, gam_contrast_rt)
p_contrast_rt
```

>>>>

cache <- TRUE
runModels <- FALSE
bestModels <- FALSE
fig.width <- see::golden_ratio(7)
fig.height <- 7

@@

```{r outliers_RT, message=FALSE, warning=FALSE, fig.width=20, fig.height=20, cache=cache}
# RT distribution
p <- df |> 
  filter(RT < 10000) |> 
  estimate_density(select = "RT", at = c("Participant", "Block")) |>
  group_by(Participant) |>
  normalize(select = "y") |>
  ungroup() |>
  mutate(Participant = fct_relevel(Participant, as.character(dfsub$Participant))) |> 
  mutate(color = ifelse(Participant %in% outliers, "red", ifelse(Participant %in% partial_outliers, "orange", "blue"))) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(data = normalize(estimate_density(filter(df, RT < 10000), select = "RT"), select = "y"), alpha = 0.2) +
  geom_line(aes(color = color, group = interaction(Participant, Block), linetype = Block)) +
  geom_vline(xintercept = 125, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("red" = "#F44336", "orange" = "#FF9800", "blue" = "blue"), guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  coord_cartesian(xlim = c(0, 3000)) +
  theme_modern() +
  theme(axis.text.y = element_blank()) +
  facet_wrap(~Participant) +
  labs(y = "", x = "Reaction Time (ms)")
# p
# ggsave("figures/outliers.png", p, width=25, height=25)

@@

save(model_delboeuf_err, file="models/model_delboeuf_err.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, eval=TRUE}
load("models/model_delboeuf_err.RData")
load("models/gam_delboeuf_err.RData")

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_delboeuf_err <- plot_model_err(data, model_delboeuf_err, gam_delboeuf_err)
```

@@

save(model_delboeuf_rt, file="models/model_delboeuf_rt.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_delboeuf_rt.RData")
load("models/gam_delboeuf_rt.RData")

@@

```{r message=FALSE, warning=FALSE, cache=cache}
plot_ppcheck(model_delboeuf_rt, gam_delboeuf_rt)

@@

```{r message=FALSE, warning=FALSE, cache=cache, fig.height=fig.height*2}
p_delboeuf <- plot_all(data, p_delboeuf_err, p_delboeuf_rt)
p_delboeuf
```

@@

save(model_ebbinghaus_err, file="models/model_ebbinghaus_err.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_ebbinghaus_err.RData")
load("models/gam_ebbinghaus_err.RData")

@@

```{r message=FALSE, warning=FALSE, cache=cache}
p_ebbinghaus_err <- plot_model_err(data, model_ebbinghaus_err, gam_ebbinghaus_err)
```

@@

```{r m_rt_ebbinghaus, message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  RT ~ Illusion_Effect / (sqrt(Illusion_Difference) * abs(Illusion_Strength)) +
    poly(ISI, 2) + 
    (1 + Illusion_Effect / (sqrt(Illusion_Difference) * abs(Illusion_Strength)) | Participant),
  sigma ~ Illusion_Effect / (sqrt(Illusion_Difference) * abs(Illusion_Strength)) + 
    poly(ISI, 2) + (1 | Participant),
  beta ~ Illusion_Effect / (sqrt(Illusion_Difference) * abs(Illusion_Strength)) + 
    poly(ISI, 2) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_ebbinghaus_rt, file="models/model_ebbinghaus_rt.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
load("models/model_ebbinghaus_rt.RData")
load("models/gam_ebbinghaus_rt.RData")

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
plot_ppcheck(model_ebbinghaus_rt, gam_ebbinghaus_rt)

p_ebbinghaus_rt <- plot_model_rt(data, model_ebbinghaus_rt, gam_ebbinghaus_rt)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, fig.height=fig.height*2, eval=TRUE}
p_ebbinghaus <- plot_all(data, p_ebbinghaus_err, p_ebbinghaus_rt)
p_ebbinghaus
```

@@

save(model_rodframe_err, file="models/model_rodframe_err.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_rodframe_err.RData")
load("models/gam_rodframe_err.RData")
```

```{r message=FALSE, warning=FALSE, cache=cache}
p_rodframe_err <- plot_model_err(data, model_rodframe_err, gam_rodframe_err)
```

@@

```{r m_rt_rodframe, message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  RT ~ Illusion_Effect / (logmod(Illusion_Difference) * logmod(abs(Illusion_Strength))) +
    poly(ISI, 2) + 
    (1 + Illusion_Effect / (logmod(Illusion_Difference) * logmod(abs(Illusion_Strength))) | Participant),
  sigma ~ Illusion_Effect / (logmod(Illusion_Difference) * logmod(abs(Illusion_Strength))) + 
    poly(ISI, 2) + (1 | Participant),
  beta ~ Illusion_Effect / (logmod(Illusion_Difference) * logmod(abs(Illusion_Strength))) + 
    poly(ISI, 2) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_rodframe_rt, file="models/model_rodframe_rt.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
load("models/model_rodframe_rt.RData")
load("models/gam_rodframe_rt.RData")

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
plot_ppcheck(model_rodframe_rt, gam_rodframe_rt)

p_rodframe_rt <- plot_model_rt(data, model_rodframe_rt, gam_rodframe_rt)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, fig.height=fig.height*2, eval=TRUE}
p_rodframe <- plot_all(data, p_rodframe_err, p_rodframe_rt)
p_rodframe
```

@@

save(model_verticalhorizontal_err, file="models/model_verticalhorizontal_err.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_verticalhorizontal_err.RData")
load("models/gam_verticalhorizontal_err.RData")

# parameters::parameters(model_verticalhorizontal_err)
```

```{r message=FALSE, warning=FALSE, cache=cache}
p_verticalhorizontal_err <- plot_model_err(data, model_verticalhorizontal_err, gam_verticalhorizontal_err)
```

@@

```{r m_rt_verticalhorizontal, message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  RT ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) +
    poly(ISI, 2) + 
    (1 + Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) | Participant),
  sigma ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) + 
    poly(ISI, 2) + (1 | Participant),
  beta ~ Illusion_Effect / (sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength))) + 
    poly(ISI, 2) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_verticalhorizontal_rt, file="models/model_verticalhorizontal_rt.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
load("models/model_verticalhorizontal_rt.RData")
load("models/gam_verticalhorizontal_rt.RData")

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
p_verticalhorizontal_rt <- plot_model_rt(data, model_verticalhorizontal_rt, gam_verticalhorizontal_rt)
```

```{r message=FALSE, warning=FALSE, cache=cache, fig.height=fig.height*2, eval=TRUE}
p_verticalhorizontal <- plot_all(data, p_verticalhorizontal_err, p_verticalhorizontal_rt)
p_verticalhorizontal
```

@@

model_zollner_err <- brms::brm(formula,
  data = data,
  refresh = 100
)

save(model_zollner_err, file="models/model_zollner_err.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_zollner_err.RData")
load("models/gam_zollner_err.RData")

# parameters::parameters(model_zollner_err)
```

```{r message=FALSE, warning=FALSE, cache=cache}
p_zollner_err <- plot_model_err(data, model_zollner_err, gam_zollner_err)
```

@@

```{r m_rt_zollner, message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  RT ~  Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) +
    poly(ISI, 2) + 
    (1 + Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) | Participant),
  sigma ~  Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) +
    poly(ISI, 2) + (1 | Participant),
  beta ~ Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) +
    poly(ISI, 2) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_zollner_rt, file="models/model_zollner_rt.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
load("models/model_zollner_rt.RData")
load("models/gam_zollner_rt.RData")

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
p_zollner_rt <- plot_model_rt(data, model_zollner_rt, gam_zollner_rt)
```

```{r message=FALSE, warning=FALSE, cache=cache, fig.height=fig.height*2, eval=TRUE}
p_zollner <- plot_all(data, p_zollner_err, p_zollner_rt)
p_zollner
```

@@

save(model_white_err, file="models/model_white_err.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_white_err.RData")
load("models/gam_white_err.RData")
```

```{r message=FALSE, warning=FALSE, cache=cache}
p_white_err <- plot_model_err(data, model_white_err, gam_white_err)
```

@@

```{r m_rt_white, message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
formula <- brms::bf(
  RT ~ Illusion_Effect / (logmod(Illusion_Difference) * abs(Illusion_Strength)) +
    poly(ISI, 2) + 
    (1 + Illusion_Effect / (logmod(Illusion_Difference) * abs(Illusion_Strength)) | Participant),
  sigma ~ Illusion_Effect / (logmod(Illusion_Difference) * abs(Illusion_Strength)) +
    poly(ISI, 2) + (1 | Participant),
  beta ~ Illusion_Effect / (logmod(Illusion_Difference) * abs(Illusion_Strength)) +
    poly(ISI, 2) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_white_rt, file="models/model_white_rt.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
load("models/model_white_rt.RData")
load("models/gam_white_rt.RData")

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
p_white_rt <- plot_model_rt(data, model_white_rt, gam_white_rt)
```

```{r message=FALSE, warning=FALSE, cache=cache, fig.height=fig.height*2, eval=TRUE}
p_white <- plot_all(data, p_white_err, p_white_rt)
p_white
```

@@

save(model_mullerlyer_err, file="models/model_mullerlyer_err.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_mullerlyer_err.RData")
load("models/gam_mullerlyer_err.RData")
```

```{r message=FALSE, warning=FALSE, cache=cache}
p_mullerlyer_err <- plot_model_err(data, model_mullerlyer_err, gam_mullerlyer_err)
```

@@

```{r m_rt_mullerlyer, message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
formula <- brms::bf(
  RT ~ Illusion_Effect / (sqrt(Illusion_Difference) * abs(Illusion_Strength)) +
    poly(ISI, 2) + 
    (1 + Illusion_Effect / (sqrt(Illusion_Difference) * abs(Illusion_Strength)) | Participant),
  sigma ~ Illusion_Effect / (sqrt(Illusion_Difference) * abs(Illusion_Strength)) +
    poly(ISI, 2) + (1 | Participant),
  beta ~ Illusion_Effect / (sqrt(Illusion_Difference) * abs(Illusion_Strength)) + 
    poly(ISI, 2) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_mullerlyer_rt, file="models/model_mullerlyer_rt.Rdata")
# parameters::parameters(model_white_err)
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
load("models/model_mullerlyer_rt.RData")
load("models/gam_mullerlyer_rt.RData")

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
p_mullerlyer_rt <- plot_model_rt(data, model_mullerlyer_rt, gam_mullerlyer_rt)
```

@@

save(model_ponzo_err, file="models/model_ponzo_err.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_ponzo_err.RData")
load("models/gam_ponzo_err.RData")
```

```{r message=FALSE, warning=FALSE, cache=cache}
p_ponzo_err <- plot_model_err(data, model_ponzo_err, gam_ponzo_err)
```

@@

save(model_ponzo_rt, file="models/model_ponzo_rt.Rdata")
# parameters::parameters(model_white_err)
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
load("models/model_ponzo_rt.RData")
load("models/gam_ponzo_rt.RData")

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
p_ponzo_rt <- plot_model_rt(data, model_ponzo_rt, gam_ponzo_rt)
```

@@

save(model_poggendorff_err, file="models/model_poggendorff_err.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_poggendorff_err.RData")
load("models/gam_poggendorff_err.RData")
```

```{r message=FALSE, warning=FALSE, cache=cache}
p_poggendorff_err <- plot_model_err(data, model_poggendorff_err, gam_poggendorff_err)
```

@@

```{r m_rt_poggendorff, message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
formula <- brms::bf(
  RT ~ Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) +
    poly(ISI, 2) + 
    (1 + Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) | Participant),
  sigma ~ Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) + 
    poly(ISI, 2) + (1 | Participant),
  beta ~ Illusion_Effect / (cbrtmod(Illusion_Difference) * abs(Illusion_Strength)) + 
    poly(ISI, 2) + (1 | Participant),
  family = "exgaussian"
)

@@

save(model_ponzo_rt, file="models/model_poggendorff_rt.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
load("models/model_poggendorff_rt.RData")
load("models/gam_poggendorff_rt.RData")

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
p_poggendorff_rt <- plot_model_rt(data, model_poggendorff_rt, gam_poggendorff_rt)
```

@@

model_contrast_err <- brms::brm(formula,
  data = data,
  refresh = 100
)

@@

save(model_contrast_err, file="models/model_contrast_err.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache}
load("models/model_contrast_err.RData")
load("models/gam_contrast_err.RData")
```

```{r message=FALSE, warning=FALSE, cache=cache}
p_contrast_err <- plot_model_err(data, model_contrast_err, gam_contrast_err)
```

@@

save(model_contrast_rt, file="models/model_contrast_rt.Rdata")
```

##### Model Inspection

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
load("models/model_contrast_rt.RData")
load("models/gam_contrast_rt.RData")

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=TRUE}
p_contrast_rt <- plot_model_rt(data, model_contrast_rt, gam_contrast_rt)
```
